---
title: "Herszenhorn Gov 50 Final Project"
author: "Miles Herszenhorn"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---


```{r}

library(tidyverse)
library(foreign)
library(readxl)
library(janitor)

data <- read_xlsx("data.xlsx") |>
  select(`20_Autonomy:_selecting_stories`, `80_Influences:_government_officials`,
         `141_Editorial_rank_(junior/senior_manager)`, 
         `143_Channel:_Daily_newspaper`, `144_Channel:_Weekly_newspaper`) |>
  clean_names() |>
  rename(
    autonomy = x20_autonomy_selecting_stories,
    government_influence = x80_influences_government_officials,
    rank = x141_editorial_rank_junior_senior_manager,
    daily = x143_channel_daily_newspaper,
    weekly = x144_channel_weekly_newspaper
  ) |>
  mutate(
    daily = case_when(
      daily == 2 ~ 1,
      daily == 1 ~ 0,
      TRUE ~ 0
    ),
    weekly = case_when(
      weekly == 2 ~ 1,
      weekly == 1 ~ 0,
      TRUE ~ 0
    )
  )

```

## Introduction

Journalism, also known as the Fourth Estate, is commonly considered integral to 
democracy due to its ability to serve as an independent source of information 
and for its ability to hold power to account. Some of the best reporting in 
which journalists successfully held power to account occurred in regards to 
revealing information to the public that politicians wish stayed secret. Other 
times, journalists published articles that held governmental officials 
accountable for their actions. The author of this project would aruge that the 
best journalism occurs when reporters are able to operated independently from 
the influence of governmental officials on their work.

This project seeks to answer that important question by studying whether 
journalism can be corrupted and influenced by government officials who are 
seeking to put constraints on the types of articles that news publications 
produce. By studying whether the perception of more government influence impacts
the autonomy journalists have to select their own stories, this might help 
underscore the importance of editorial independence on journalism. The 
hypothesis is that journalists indeed feel like they have less autonomy to 
select their own stories for publication when they feel more influenced by
governmental officials. This project will hopefully help determine the extent to
which the perception of influence by government officials can impact reporters'
ability to tell their own stories.

## Data Used in Project

The data source used in this project comes from the Worlds of Journalism study,
an academic project that attempts to regularly assess the state of journalism in
the world. The data set is from a cross-sectional study of journalists in dozens
of countries around the world. The data source being used for the purposes of 
this project had more than 27,000 responses from reporters in many countries 
across the globe. 

The study, which was conducted as a survey, asked journalists in countries 
around the world a series a questions about their profession, including about 
what they viewed as potentially serving as an influence on them, what might 
restrict their autonomy, and what the surveyed reporters emphasize the most when
it comes to journalistic ethics. The data also clarified the demogrpahics of its
respondents as well as the types of media outlets that they worked for.


## Results

```{r}
data |>
  ggplot(aes(x = autonomy)) +
  geom_bar() +
  labs(x = "Amount of Autonomy", y = "Number of Respondents",
       title = "Level of Autonomy in Selecting Stories")
```


```{r}
data |>
  ggplot(aes(x = government_influence, y = autonomy)) +
  geom_jitter(alpha = 0.3)+
  labs(x = "Influence by Governmental Officials", y = "Level of Autonomy",
       title = "Perceived Autonomy by Journalists to Select Stories")
```

```{r}
data |>
  ggplot(aes(x = as.factor(government_influence), y = autonomy)) +
  geom_boxplot()+
  labs(x = "Autonomy to Select Stories", y = "Influence from Governmental Officials",
  title = "Level of Autonomy Compared to Influence by Governmental Officials")
```


```{r}
fit <- lm(autonomy ~ daily + weekly + government_influence, data = data)
summary(fit)
```


```{r}
library(modelsummary)
var_labels <- c(
  "(Intercept)" = "Intercept", 
  "daily" = "Daily Newspaper", 
  "weekly" = "Weekly Newspaper",
  "government_influence" = "Influence of Government Officials")
modelsummary::modelsummary(fit,
            statistic = c("s.e. = {std.error}",
            "p = {p.value}"),
            coef_map = var_labels,
            gof_map = c("nobs", "r.squared", "adj.r.squared"))
            
```

After having completed the main analysis of data in this project, it can be 
concluded that the null hypothesis can be rejected because it is a small p-value
and close to zero (<0.001). The null hypothesis is thus rejected and leads us to
conclude that the conclusions we had found in this project are likely to not
have occurred accidentally or incidentally, and allows us to report that the
results are likely true.

As a result, we can determine that journalists who feel that there is
heightened influence of government officials are more likely to report that they
feel as if they have less autonomy to select the stories that they would like to
publish. But due to the fact that there are several factors that could go into 
determining whether or not stories get selected for publication, this project
also took into account the differences in publication, taking newspapers that
publish daily and newspapers that publish weekly as potential confounders. This
allowed us to check whether journalists who feel like they have less autonomy to
select their stories feel that way due to the regularity of their outlet's
publication schedule as opposed to the influence of government officials.

## Conclusion

The low reported p_value and the low reported standard error allow us
to conclude that the null hypothesis is rejected, thus affirming our original
hypothesis at the start of the project. It is likely that the more journalists
feel influenced by governmental officials, the more journalists feel like they
have less autonomy to select their own stories. While this study attempted to
take into account regularity of publication, there could have been several other
factors that would go into the response to the project's questions, including a
news outlets' business model and whether a journalist having the autonomy to
select their own stories could run contrary to the business model (i.e. 
publications that rely on publishing click bait to turn a profit.) With more
time and resources, this project would seek to take more of these confounding 
facotors into account and address them more comprehensively in a future study.


